Notes on scheduling the SAA2019 meeting

### 2017-11-05 analysis/paper/saa2018_nonposter_sessions_while_loop.Rmd
why did I miss 3115, 3147, 3175, 3116, 3152, 3162? I don't know. Perhapsthere is no perfect solution

    get_a_session <- z7[j, ]

@@

@@

She's ok, great!

@@

She's ok, oon Fr-morning

@@

We have `r Su_morning_spare_hours` hours unused on Sunday morning. Heaps of space. So let's move Session 2929 to Sunday morning:

```{r}
sessions_in_day_parts_data_with_all_names_df <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  mutate(day_part_from_while.y = if_else(`Session Id` == 2929, 
                                         "Su-morning", 
                                         day_part_from_while.y))

@@

@@

- Posters

>>>>

    # randomly reorder the rows to see if we can solve a problem
    # z7 <- z7[sample(nrow(z7)),]
    get_a_session <- z7[j, ]

@@

Did we get all sessions allocated to a day-part?

```{r}
sessions_we_missed <- 
  setdiff(unique(all_nonposter_sessions$`Session Id`),
          unique(all_of_the_day_parts$`Session Id`))
```

We missed `r length(sessions_we_missed)` sessions: `r sessions_we_missed`.

@@

Sa-afternoon and Sa-morning, she's ok, great!

@@

She's ok, on Fr-morning

@@

We have `r Su_morning_spare_hours` hours unused on Sunday morning. Heaps of space. So let's move Session 2929 to Sunday morning. Don't forget to update the computed slot value so it gets it's own slot.

# what is the max computed_slot for Su-morning?
max_computed_slot_Su_morning <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(day_part_from_while.y == "Su-morning") %>% 
  summarise(max_computed_slot_Su_morning = max(computed_slot)) %>% 
  pull(max_computed_slot_Su_morning)

sessions_in_day_parts_data_with_all_names_df <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  mutate(day_part_from_while.y = if_else(`Session Id` == 2929, 
                                         "Su-morning", 
                                         day_part_from_while.y)) %>% 
  mutate(computed_slot = ifelse(`Session Id` == 2929, 
                                         max_computed_slot_Su_morning + 1, 
                                         computed_slot))

@@

# check to see if there are conflicts with names, should be 0
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(day_part_from_while.y == "Su-morning") %>%
  group_by(`Session Id`, uid.y)  %>% 
  add_tally() %>% 
  distinct(`Session Id`) %>% 
  group_by(uid.y) %>% 
  filter(n() > 1 )

# how many slots in Sun?

# available?
total_cap #28

# used?
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(day_part_from_while.y == "Su-morning") %>% 
  distinct(computed_slot) %>% 
  max()
# 21

- AB says

>-  row 10 has session 2929 sharing with session 3165. But session 2929 needs 16 slots, which is 4 hours.

Problem was that I forgot to update the computed slot value. Fixed now.

>- Missing 3115, 3147, 3175, 3116, 3152, 3162

all_nonposter_sessions %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162")) 
# yes, there

# how many sessions""
length(unique(all_nonposter_sessions$`Session Id`)) #  271

all_nonposter_sessions_with_session_durations  %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162")) 
# yes

org_and_gen_session_durations  %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162")) 
# yes

all_of_the_day_parts  %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162")) 
# not there

sessions_in_day_parts_data_with_all_names_df %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162"))
# not there

# how many sessions?
length(unique(sessions_in_day_parts_data_with_all_names_df$`Session Id`)) # 265

# are these sessions very long?
hours_of_missing_sessions <- 
all_nonposter_sessions %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162"))  %>% 
  group_by(`Session Id`) %>% 
  tally() %>% 
  mutate(minutes = n * 15) %>% 
  mutate(hours = minutes / 60)
# nope
total_hours_missing <-  sum(hours_of_missing_sessions$hours)

# what are they about?
all_nonposter_sessions %>% 
  filter(`Session Id` %in% missing_sessions) %>% 
  select(Abstract, Title)
# no title or abstracts!

# So, no idea what's going on with these. Let's see if there are any problems with putting them on Sunday
missing_sessions_details <- 
  all_nonposter_sessions %>% 
  filter(`Session Id` %in% c("3115", "3147", "3175", "3116", "3152", "3162")) %>% 
  mutate(uid.y = uid)

# are any people in more than one session Sunday? yes
# what about all the day-parts with spare hours
clashes_on_day_x <- function(day) {
  sessions_in_day_parts_data_with_all_names_df %>% 
 filter(day_part_from_while.y == day) %>% 
  bind_rows(missing_sessions_details) %>% 
  group_by(`Session Id`, uid.y)  %>% 
  add_tally() %>% 
  distinct(`Session Id`) %>% 
  group_by(uid.y) %>% 
  filter(n() > 1 )
}

total_cap_remaining <- 
  total_cap %>% 
  mutate(hours_unused =  total_capacity - hours_of_sessions) %>% 
  select(day_part, hours_unused)

day_with_spare_hours <- c("Fr-morning",
                          "Fr-afternoon",
                          "Sa-morning",
                          "Sa-afternoon",
                          "Su-morning")

total_cap_remaining %>% 
  mutate(clashes = map(day_part, clashes_on_day_x)) %>% 
  mutate(n_clashes = map_int(.$clashes, ~nrow(.x)))

# Looks like Th-morning has no clashes, double-check, should be 0

 sessions_in_day_parts_data_with_all_names_df %>% 
  filter(day_part_from_while.y ==  "Th-morning") %>% 
  bind_rows(missing_sessions_details) %>% 
  group_by(`Session Id`, uid.y)  %>% 
  add_tally() %>% 
  distinct(`Session Id`) %>% 
  group_by(uid.y) %>% 
  filter(n() > 1 )
```

Seems that Th-morning is a good place to put these missing sessions. So let's do that. We'll have to double-up in some slots

```{r}
# find out how many hours we have for each slot on th-morn
slot_on_thu_morn_with_less_than_4_h <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(day_part_from_while.y == "Th-morning") %>% 
  distinct(`Session Id`, .keep_all = TRUE) %>% 
  group_by(computed_slot) %>% 
  summarise(total_duration = sum(session_time_allowed.y)) %>% 
  filter(total_duration < 4) %>% 
  mutate(minutes = total_duration * 60) %>% 
  mutate(minutes_free = (4*60) - minutes)

# how many hours do we need to put in there?
minutes_of_missing_sessions <- 
  hours_of_missing_sessions$minutes

# # what is the max computed_slot for Su-morning?
# max_computed_slot_Th_morning <- 
# sessions_in_day_parts_data_with_all_names_df %>% 
#   filter(day_part_from_while.y == "Th-morning") %>% 
#   summarise(max_computed_slot_Th_morning = max(computed_slot)) %>% 
#   pull(max_computed_slot_Th_morning)
# 
# # assign missing sessions to Th morn, update slots
# missing_sessions_details <- 
# missing_sessions_details %>% 
#   mutate(day_part_from_while.y = "Th-morning")
# 
# missing_sessions_details_indices  <- 
# missing_sessions_details %>% 
#   group_by(`Session Id`) %>% 
#   group_indices()
# 
# # update computed slot
# missing_sessions_details <- 
#   missing_sessions_details %>% 
#     mutate(computed_slot = missing_sessions_details_indices + max_computed_slot_Th_morning) 
```

We can't put them all on Th morn, there's not slot with enough free space to fit more than one of the missing sessions in

# # bind to rest of the papers
# sessions_in_day_parts_data_with_all_names_df <- 
#   bind_rows(sessions_in_day_parts_data_with_all_names_df ,
#             missing_sessions_details)
#             
# 
# # check it, should be Th-morning
# check_missing_sessions_to_thu_morning <- 
# sessions_in_day_parts_data_with_all_names_df %>% 
#   filter(`Session Id` %in% missing_sessions) %>% 
#   select(day_part_from_while.y) %>% 
#   unique()
# 
# # check for conflicts with names
#  sessions_in_day_parts_data_with_all_names_df %>% 
#   filter(day_part_from_while.y ==  "Th-morning") %>% 
#   group_by(`Session Id`, uid.y)  %>% 
#   add_tally() %>% 
#   distinct(`Session Id`) %>% 
#   group_by(uid.y) %>% 
#   filter(n() > 1 )

@@
